paper

### 2024-09-13 paper.qmd
.

```{r}
# Load necessary packages
library(LimROTS)
library(parallel)
# Load the dataset
data("UPS1.Case0")
print(UPS1.Case0)
# Set random seed for reproducibility
set.seed(1234, kind = "default")
# Set metadata and formula for LimROTS analysis
meta.info <- "Conc."
B <- 1000  # Number of bootstrap samples
K <- dim(UPS1.Case0)[1]/4  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "Conc."
formula.str <- "~ 0 + Conc."  # Formula for group comparison
# Run LimROTS analysis with trend and robust settings enabled
limrots.result <- LimROTS(data.exp = UPS1.Case0, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE)
saveRDS(limrots.result, "../LimROTS paper/UPS1.Case0.LimROTS.rds")
```

@@

```{r}
# Load necessary packages
library(LimROTS)
library(parallel)
# Load the dataset
data("UPS1.Case0")
print(UPS1.Case0)
# Set random seed for reproducibility
set.seed(1234, kind = "default")
# Set metadata and formula for LimROTS analysis
meta.info <- "Conc."
B <- 1000  # Number of bootstrap samples
K <- dim(UPS1.Case0)[1]/4  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "Conc."
formula.str <- "Conc."
# Run LimROTS analysis with trend and robust settings enabled
rots.result <- LimROTS(data.exp = UPS1.Case0, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE, n.ROTS = TRUE)
saveRDS(rots.result, "../LimROTS paper/UPS1.Case0.ROTS.rds")
```

@@

```{r}
library(limma)
library(SummarizedExperiment, quietly = T, warn.conflicts = T)
data("UPS1.Case0")
data <- assay(UPS1.Case0)
formula.str <- "~ 0 + Conc."
meta.info <- data.frame(colData(UPS1.Case0), check.names = FALSE, row.names = row.names(colData(UPS1.Case0)))
meta.info$sample.id <- NULL
design.matrix <- model.matrix(formula(formula.str), data = meta.info)
colnames(design.matrix) <- make.names(colnames(design.matrix))
fit <- lmFit(data, design.matrix)
cont_matrix <- makeContrasts("Conc.1-Conc.2",  levels=design.matrix)
fit2 <- contrasts.fit(fit, cont_matrix)
fit.ebayes <- eBayes(fit2, trend=TRUE, robust=TRUE)
limma.result <- topTable(fit.ebayes, coef="Conc.1-Conc.2" , number = "Inf")
saveRDS(limma.result, "../LimROTS paper/UPS1.Case0.limma.rds")
```

@@

```{r}
library(caret)

@@

```{r}
# Load necessary packages
library(LimROTS)
library(parallel)
# Load the dataset
data("UPS1.Case1")
print(UPS1.Case1)
# Set random seed for reproducibility
set.seed(1234, kind = "default")
# Set metadata and formula for LimROTS analysis
meta.info <- c("Conc." , "inj")
B <- 1000  # Number of bootstrap samples
K <- dim(UPS1.Case1)[1]/4 # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 10  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "Conc."
formula.str <- "~ 0 + Conc.+ inj + Conc.*inj"  # Formula for group comparison + injections
# Run LimROTS analysis with trend and robust settings enabled
limrots.result <- LimROTS(data.exp = UPS1.Case1, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE)
saveRDS(limrots.result, "../LimROTS paper/UPS1.Case1.LimROTS.rds")
```

@@

```{r}
# Load necessary packages
library(LimROTS)
library(parallel)
# Load the dataset
data("UPS1.Case1")
print(UPS1.Case1)
# Set random seed for reproducibility
set.seed(1234, kind = "default")
# Set metadata and formula for LimROTS analysis
meta.info <- c("Conc." , "inj")
B <- 1000  # Number of bootstrap samples
K <- dim(UPS1.Case1)[1]/4 # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "Conc."
formula.str <- "~ 0 + Conc.+ inj + Conc.*inj"  # Formula for group comparison + injections
# Run LimROTS analysis with trend and robust settings enabled
rots.result <- LimROTS(data.exp = UPS1.Case1, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE, n.ROTS = TRUE)
saveRDS(rots.result, "../LimROTS paper/UPS1.Case1.ROTS.rds")
```

@@

```{r}
library(limma)
library(SummarizedExperiment, quietly = T, warn.conflicts = T)
data("UPS1.Case1")
data <- assay(UPS1.Case1)
formula.str <- "~ 0 + Conc.+ inj + Conc.*inj"
meta.info <- data.frame(colData(UPS1.Case1), check.names = FALSE, row.names = row.names(colData(UPS1.Case1)))
meta.info$sample.id <- NULL
design.matrix <- model.matrix(formula(formula.str), data = meta.info)
colnames(design.matrix) <- make.names(colnames(design.matrix))
fit <- lmFit(data, design.matrix)
cont_matrix <- makeContrasts("Conc.1-Conc.2",  levels=design.matrix)
fit2 <- contrasts.fit(fit, cont_matrix)
fit.ebayes <- eBayes(fit2, trend=TRUE, robust=TRUE)
limma.result <- topTable(fit.ebayes, coef="Conc.1-Conc.2" , number = "Inf")
saveRDS(limma.result, "../LimROTS paper/UPS1.Case1.limma.rds")
```

@@

```{r}

@@

```{r}
library(limma)
library(SummarizedExperiment, quietly = T, warn.conflicts = T)
data("UPS1.Case4")
data <- assay(UPS1.Case4)
formula.str <- "~ 0 + Conc. + tool + fake.batch"
meta.info <- data.frame(colData(UPS1.Case4), check.names = FALSE, row.names = row.names(colData(UPS1.Case4)))
meta.info$sample.id <- NULL
design.matrix <- model.matrix(formula(formula.str), data = meta.info)
colnames(design.matrix) <- make.names(colnames(design.matrix))
fit <- lmFit(data, design.matrix)
cont_matrix <- makeContrasts("Conc.1-Conc.2",  levels=design.matrix)
fit2 <- contrasts.fit(fit, cont_matrix)
fit.ebayes <- eBayes(fit2, trend=TRUE, robust=TRUE)
limma.result <- topTable(fit.ebayes, coef="Conc.1-Conc.2" , number = "Inf")
saveRDS(limma.result, "../LimROTS paper/UPS1.Case2.limma.rds")
```

Run ANCOVA

```{r}
formula.str <- "~ Conc. + tool + fake.batch"
data("UPS1.Case4")
data <- assay(UPS1.Case4)
meta.info <- data.frame(colData(UPS1.Case4), check.names = FALSE, row.names = row.names(colData(UPS1.Case4)))
meta.info$sample.id <- NULL
ancova.result <- data.frame()
for(i in 1:nrow(data)){
  df.temp <- data[i,]
  data.temp <- data.frame(response = as.numeric(df.temp) , Conc. = meta.info$Conc.,
                     tool = meta.info$tool, fake.batch = meta.info$fake.batch )
  ancova_model <- lm(formula(paste("response", formula.str)), data = data.temp)
  coef_table <- anova(ancova_model)
  coef_table <- data.frame(coef_table)
  significant_groups <- coef_table[rownames(coef_table) == "Conc." , ]
  ancova.result <- rbind(ancova.result, data.frame(protein = row.names(data)[i], p.value =significant_groups[, 5] ))
}
ancova.result$FDR <- p.adjust(ancova.result$p.value, method = "fdr")

@@

```{r}
library(caret)

>>>>

```{r results = "hide" , message = FALSE, warning = FALSE}
# Load necessary packages
library(LimROTS)
library(parallel)
# Load the dataset
data("UPS1.Case0")
print(UPS1.Case0)
# Set random seed for reproducibility
set.seed(1234, kind = "default")
# Set metadata and formula for LimROTS analysis
meta.info <- "Conc."
B <- 1000  # Number of bootstrap samples
K <- dim(UPS1.Case0)[1]/4  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "Conc."
formula.str <- "~ 0 + Conc."  # Formula for group comparison
# Run LimROTS analysis with trend and robust settings enabled
limrots.result <- LimROTS(data.exp = UPS1.Case0, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE)
saveRDS(limrots.result, "../LimROTS paper/UPS1.Case0.LimROTS.rds")
```

@@

```{r results = "hide" , message = FALSE, warning = FALSE}
# Load necessary packages
library(LimROTS)
library(parallel)
# Load the dataset
data("UPS1.Case0")
print(UPS1.Case0)
# Set random seed for reproducibility
set.seed(1234, kind = "default")
# Set metadata and formula for LimROTS analysis
meta.info <- "Conc."
B <- 1000  # Number of bootstrap samples
K <- dim(UPS1.Case0)[1]/4  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "Conc."
formula.str <- "Conc."
# Run LimROTS analysis with trend and robust settings enabled
rots.result <- LimROTS(data.exp = UPS1.Case0, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE, n.ROTS = TRUE)
saveRDS(rots.result, "../LimROTS paper/UPS1.Case0.ROTS.rds")
```

@@

```{r results = "hide" , message = FALSE, warning = FALSE}
library(limma)
library(SummarizedExperiment, quietly = T, warn.conflicts = T)
data("UPS1.Case0")
data <- assay(UPS1.Case0)
formula.str <- "~ 0 + Conc."
meta.info <- data.frame(colData(UPS1.Case0), check.names = FALSE, row.names = row.names(colData(UPS1.Case0)))
meta.info$sample.id <- NULL
design.matrix <- model.matrix(formula(formula.str), data = meta.info)
colnames(design.matrix) <- make.names(colnames(design.matrix))
fit <- lmFit(data, design.matrix)
cont_matrix <- makeContrasts("Conc.1-Conc.2",  levels=design.matrix)
fit2 <- contrasts.fit(fit, cont_matrix)
fit.ebayes <- eBayes(fit2, trend=TRUE, robust=TRUE)
limma.result <- topTable(fit.ebayes, coef="Conc.1-Conc.2" , number = "Inf")
saveRDS(limma.result, "../LimROTS paper/UPS1.Case0.limma.rds")
```

@@

```{r results = "hide" , message = FALSE, warning = FALSE}
library(caret, quietly = T, warn.conflicts = T)

@@

```{r results = "hide" , message = FALSE, warning = FALSE}
# Load necessary packages
library(LimROTS)
library(parallel)
# Load the dataset
data("UPS1.Case1")
print(UPS1.Case1)
# Set random seed for reproducibility
set.seed(1234, kind = "default")
# Set metadata and formula for LimROTS analysis
meta.info <- c("Conc." , "inj")
B <- 1000  # Number of bootstrap samples
K <- dim(UPS1.Case1)[1]/4 # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 10  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "Conc."
formula.str <- "~ 0 + Conc.+ inj + Conc.*inj"  # Formula for group comparison + injections
# Run LimROTS analysis with trend and robust settings enabled
limrots.result <- LimROTS(data.exp = UPS1.Case1, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE)
saveRDS(limrots.result, "../LimROTS paper/UPS1.Case1.LimROTS.rds")
```

@@

```{r results = "hide" , message = FALSE, warning = FALSE}
# Load necessary packages
library(LimROTS)
library(parallel)
# Load the dataset
data("UPS1.Case1")
print(UPS1.Case1)
# Set random seed for reproducibility
set.seed(1234, kind = "default")
# Set metadata and formula for LimROTS analysis
meta.info <- c("Conc." , "inj")
B <- 1000  # Number of bootstrap samples
K <- dim(UPS1.Case1)[1]/4 # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "Conc."
formula.str <- "~ 0 + Conc.+ inj + Conc.*inj"  # Formula for group comparison + injections
# Run LimROTS analysis with trend and robust settings enabled
rots.result <- LimROTS(data.exp = UPS1.Case1, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE, n.ROTS = TRUE)
saveRDS(rots.result, "../LimROTS paper/UPS1.Case1.ROTS.rds")
```

@@

```{r results = "hide" , message = FALSE, warning = FALSE}
library(limma)
library(SummarizedExperiment, quietly = T, warn.conflicts = T)
data("UPS1.Case1")
data <- assay(UPS1.Case1)
formula.str <- "~ 0 + Conc.+ inj + Conc.*inj"
meta.info <- data.frame(colData(UPS1.Case1), check.names = FALSE, row.names = row.names(colData(UPS1.Case1)))
meta.info$sample.id <- NULL
design.matrix <- model.matrix(formula(formula.str), data = meta.info)
colnames(design.matrix) <- make.names(colnames(design.matrix))
fit <- lmFit(data, design.matrix)
cont_matrix <- makeContrasts("Conc.1-Conc.2",  levels=design.matrix)
fit2 <- contrasts.fit(fit, cont_matrix)
fit.ebayes <- eBayes(fit2, trend=TRUE, robust=TRUE)
limma.result <- topTable(fit.ebayes, coef="Conc.1-Conc.2" , number = "Inf")
saveRDS(limma.result, "../LimROTS paper/UPS1.Case1.limma.rds")
```

@@

```{r results = "hide" , message = FALSE, warning = FALSE}

@@

```{r results = "hide" , message = FALSE, warning = FALSE}
library(limma)
library(SummarizedExperiment, quietly = T, warn.conflicts = T)
data("UPS1.Case4")
data <- assay(UPS1.Case4)
formula.str <- "~ 0 + Conc. + tool + fake.batch"
meta.info <- data.frame(colData(UPS1.Case4), check.names = FALSE, row.names = row.names(colData(UPS1.Case4)))
meta.info$sample.id <- NULL
design.matrix <- model.matrix(formula(formula.str), data = meta.info)
colnames(design.matrix) <- make.names(colnames(design.matrix))
fit <- lmFit(data, design.matrix)
cont_matrix <- makeContrasts("Conc.1-Conc.2",  levels=design.matrix)
fit2 <- contrasts.fit(fit, cont_matrix)
fit.ebayes <- eBayes(fit2, trend=TRUE, robust=TRUE)
limma.result <- topTable(fit.ebayes, coef="Conc.1-Conc.2" , number = "Inf")
saveRDS(limma.result, "../LimROTS paper/UPS1.Case2.limma.rds")
```

## Run ANCOVA

```{r results = "hide" , message = FALSE, warning = FALSE}
formula.str <- "~ Conc. + tool + fake.batch"
data("UPS1.Case4")
data <- assay(UPS1.Case4)
meta.info <- data.frame(colData(UPS1.Case4), check.names = FALSE, row.names = row.names(colData(UPS1.Case4)))
meta.info$sample.id <- NULL
ancova.result <- data.frame()
for(i in 1:nrow(data)){
  df.temp <- data[i,]
  data.temp <- data.frame(response = as.numeric(df.temp) , Conc. = meta.info$Conc.,
                     tool = meta.info$tool, fake.batch = meta.info$fake.batch )
  ancova_model <- lm(formula(paste("response", formula.str)), data = data.temp)
  coef_table <- anova(ancova_model)
  coef_table <- data.frame(coef_table)
  significant_groups <- coef_table[rownames(coef_table) == "Conc." , ]
  ancova.result <- rbind(ancova.result, data.frame(protein = row.names(data)[i], p.value =significant_groups[, 5] ))
}
ancova.result$FDR <- p.adjust(ancova.result$p.value, method = "fdr")

@@

```{r results = "hide" , message = FALSE, warning = FALSE}
library(caret)
